\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-02-19 manuscript/manuscript.tex
small manuscript changes

We generated time series with marginal distributions $N(8, 8)$ and
\jy{why choose these two distributions?}\mc{addressed}
$\Gamma(8, 1)$, Kendall's $\tau \in \{-.75, -.5, -.25, 0, .25, .5, 
.75\}$, and
sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as
it ...
The autocorrelation $\phi$ of the series was set to \{-0.924, -0.707, 
-0.383, 0, 0.383, 0.707, 0.924\}. These
are the autocorrelations of the normal series, but after the transformation
to the marginal gamma distribution
\mc{my explanation needs work}

These distributions
were chosen to compare results on normal and non-normal
error structures. The specific parameters were chosen because the distributions 
are very similar and their
first two moments are the same.  To generate...
For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution family is normal, and when $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is gamma. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\tau$, and $n$, we replicate the method 1000 times 
to get the distribution of the p-values 
for the test when applied to samples from the same data generating process.

>>>>

We generated time series with marginal distributions $N(8, 8)$ and
\jy{why choose these two distributions?}\mc{addressed}
$\Gamma(8, 1)$, Kendall's $\tau \in \{-.75, -.5, -.25, 0, .25, .5, 
.75\}$, and
sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
measure of serial dependence as it does not vary between two different 
distributions.
The autocorrelation $\phi$ of the series was set to \{-0.924, -0.707, 
-0.383, 0, 0.383, 0.707, 0.924\}. These
are the autocorrelations of the normal series, but after the transformation
to the marginal gamma distribution, the autocorrelations are $\{-0.607, 
diverges,
-0.287, 0, 0.339, 0.668, 0.911\}$.
\mc{my explanation needs work}

These distributions
were chosen to compare results on normal and non-normal
error structures. The specific parameters were chosen because the distributions 
are very similar and their
first two moments are the same. The series were generated by marginally 
transforming the
marginal normal AR(1) series $X_t$ by
\begin{equation*}
W_t = F^{-1}[\Phi(X_t)],
\end{equation*}
where $F^{-1}(p)$ is the quantile function for the $\Gamma(8, 1)$.
For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution family is normal, and when $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is gamma. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\tau$, and $n$, we replicate the method 1000 times 
to get the distribution of the p-values 
for the test when applied to samples from the same data generating process.
